### 2024-04-03 README.Rmd
fixing readme

```{r example}
library(criticalvalue)
# devtools::load_all()

@@

dat <- data.frame(x, y, z, q)
fit <- lm(y ~ x + q + z, data = dat)
fit <- critical(fit)
summary(fit)

>>>>

```{r example}
# library(criticalvalue)
devtools::load_all()

@@

dat <- data.frame(x, y, z, q)
fit <- lm(y ~ x + q + z, data = dat)
fit <- critical(fit)
fit
summary(fit)
